Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-25 proposal/prop.tex
proposal\prop.bib Remove duplicated keys...

Over the past several years, the PI, together with other IU faculty
members and students, has formed a group whose main interest is the
study of paradigms of computing that either arise in nature or are
inspired by natural phenomena. The PI is especially interested in how
the laws of physics can inspire and guide our abstract computational
models, as well as exposing new insights into the computational
framework behind the natural world and the computability of physical
theory. Our group has been active in several areas related to the
theory behind quantum computation. Particular areas include:
mathematical foundations of quantum computation and
complexity~\cite{DBLP:journals/entcs/AltenkirchGVS07,1166040},
adiabatic quantum computing, quantum logic, classical and quantum
reversible programming languages~\cite{Sabry:2003:MQC:871895.871900},
analog computation and its limits, and optical computing. During the
last year, our discussions have revolved around formulating variants
of quantum mechanics that are computable and that are as close to
possible to classical computing. Several preliminary results have
emerged from our collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
is very excited about the potential implications of those
results. This proposal brings forth a particular aspect of this
programme related to its applications to problem areas that have
traditionally been outside the conceptual framework of programming
language research.

>>>>

Over the past several years, the PI, together with other IU faculty
members and students, has formed a group whose main interest is the
study of paradigms of computing that either arise in nature or are
inspired by natural phenomena. The PI is especially interested in how
the laws of physics can inspire and guide our abstract computational
models, as well as exposing new insights into the computational
framework behind the natural world and the computability of physical
theory. Our group has been active in several areas related to the
theory behind quantum computation. Particular areas include:
mathematical foundations of quantum computation and
complexity~\cite{AGVS2007,VAS2006},
adiabatic quantum computing, quantum logic, classical and quantum
reversible programming languages~\cite{Sabry:2003:MQC:871895.871900},
analog computation and its limits, and optical computing. During the
last year, our discussions have revolved around formulating variants
of quantum mechanics that are computable and that are as close to
possible to classical computing. Several preliminary results have
emerged from our collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
is very excited about the potential implications of those
results. This proposal brings forth a particular aspect of this
programme related to its applications to problem areas that have
traditionally been outside the conceptual framework of programming
language research.
